The importance of measurement uncertainty in ecological management

### 2018-01-16 appendix/appendix_harvestfirst.Rmd
WIP

```{r}
sims <- bind_rows(static_sims, pomdp_sims) %>%
    left_join(meta) %>%    ## combine output with scenarios
    mutate(state = states[state], action = actions[action]) # index -> value

sims <- sims %>% select(time, state, rep, method, sigma_m, sigma_g)

>>>>

```{r}
sims <- bind_rows(static_sims, pomdp_sims) %>%
    left_join(meta) %>%  ## include scenario information (sigmas; etc)
    mutate(state = states[state], action = actions[action]) %>%
    select(time, state, rep, method, sigma_m, sigma_g, value)

### 2018-01-16 manuscripts/manuscript.Rmd
WIP

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors
```

```{r suggested_libs, message=FALSE}
#knitr::opts_chunk$set( dev="CairoPDF")
knitr::opts_chunk$set( dev="cairo_pdf")
library(hrbrthemes)
hrbrthemes::import_roboto_condensed() 
library(ggplot2)
library(Cairo)
library(extrafont)
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

```{r}
log_dir <- "../data" # solution files here
```

@@

```{r load_data, message=FALSE, warning=FALSE}
sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnn")
det_sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/det_sims.csv"))
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))

@@

```{r fig.width=7,fig.height=3.5, fig.cap=""}
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "pgy")) %>%
  mutate(policy = fct_recode(policy,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) -> policy_df
policy_df %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```
```{r fig.width=7,fig.height=3.5, fig.cap=""}
policy_df %>%
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
```

```{r optional_plot_fonts, message=FALSE}
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

```{r plot_colors}
#palette <- ggthemes::ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

```{r load_data, message=FALSE, warning=FALSE}
log_dir <- "../data" # solution files here

sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnn")
det_sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/det_sims.csv"))
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))

@@

@@

```{r fig.width=7,fig.height=7, fig.cap=""}
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "pgy")) %>%
  mutate(policy = fct_recode(policy,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) -> policy_df
harvest <- policy_df %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8)) + 
  ggtitle("Harvest view") + 
  theme(legend.position="none")

escapement <- policy_df %>%
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8)) +
  ggtitle("Escapement view") + 
  theme(legend.position = "bottom")

gridExtra::grid.arrange(harvest, escapement, 
                        layout_matrix = rbind(c(1,1), c(2,2)))
